---
title: |
  | FPREN Infrastructure Access Request
  | University of Florida Information Technology
subtitle: |
  | Firewall Rules, SSL Certificate, and GatorLink SSO Integration
  | Florida Public Radio Emergency Network
author: |
  | Lawrence Bornacelli
  | College of Journalism and Communications / WUFT
  | University of Florida
  | lawrence.bornace@ufl.edu
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 3
    number_sections: true
    fig_caption: true
    keep_tex: false
    includes:
      in_header: null
geometry: "margin=1in"
fontsize: 11pt
linestretch: 1.2
header-includes:
  - \usepackage{xcolor}
  - \usepackage{fancyhdr}
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}

  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{hyperref}
  - \definecolor{ufblue}{RGB}{0, 33, 99}
  - \definecolor{uforange}{RGB}{250, 70, 22}
  - \definecolor{alertred}{RGB}{180, 30, 30}
  - \definecolor{statusgreen}{RGB}{30, 130, 50}
  - \definecolor{lightgray}{RGB}{245, 245, 245}
  - \definecolor{midgray}{RGB}{200, 200, 200}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[L]{\textcolor{ufblue}{\small FPREN --- UF IT Infrastructure Access Request}}
  - \fancyhead[R]{\textcolor{ufblue}{\small \today}}
  - \fancyfoot[C]{\textcolor{midgray}{\small --- \thepage\ ---}}
  - \fancyfoot[L]{\textcolor{midgray}{\small CONFIDENTIAL --- UF Internal Use Only}}
  - \renewcommand{\headrulewidth}{0.4pt}
  - \renewcommand{\footrulewidth}{0.4pt}
  - \hypersetup{colorlinks=true, linkcolor=ufblue, urlcolor=ufblue, citecolor=ufblue}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.pos = "H"
)

# Load libraries
library(knitr)
library(kableExtra)

# Optional: read live connectivity data if available
live_data <- NULL
if (file.exists("/tmp/fpren_access_check.json")) {
  tryCatch({
    live_data <- jsonlite::fromJSON("/tmp/fpren_access_check.json")
  }, error = function(e) {
    live_data <- NULL
  })
}
```

\newpage

<!-- ============================================================ -->
<!--  COVER BANNER                                                -->
<!-- ============================================================ -->

\vspace*{0.5cm}

\begin{center}
\colorbox{ufblue}{\parbox{\textwidth}{
  \vspace{0.6cm}
  \begin{center}
  \textcolor{white}{\Huge \textbf{FPREN}}\\[0.3cm]
  \textcolor{uforange}{\large \textbf{Florida Public Radio Emergency Network}}\\[0.2cm]
  \textcolor{white}{\normalsize University of Florida --- College of Journalism and Communications / WUFT}\\[0.2cm]
  \textcolor{white}{\normalsize UF VM: \texttt{128.227.67.234} \quad|\quad Ubuntu 24.04 LTS}\\[0.4cm]
  \textcolor{white}{\small \textbf{Infrastructure Access Request}}\\[0.1cm]
  \textcolor{uforange}{\small Firewall Rules \textbullet{} SSL Certificate \textbullet{} GatorLink SSO Integration}
  \vspace{0.6cm}
  \end{center}
}}
\end{center}

\vspace{0.8cm}

\begin{center}
\begin{tabular}{ll}
\textbf{Prepared by:}  & Lawrence Bornacelli \\
\textbf{Email:}        & \href{mailto:lawrence.bornace@ufl.edu}{lawrence.bornace@ufl.edu} \\
\textbf{Department:}   & College of Journalism and Communications / WUFT \\
\textbf{Institution:}  & University of Florida \\
\textbf{Report Date:}  & \today \\
\textbf{Submitted to:} & UF Information Technology (UF IT) \\
\textbf{Classification:} & \textcolor{alertred}{\textbf{CONFIDENTIAL --- UF Internal Use Only}} \\
\end{tabular}
\end{center}

\vspace{0.8cm}

\begin{center}
\colorbox{lightgray}{\parbox{0.92\textwidth}{
  \vspace{0.3cm}
  \textbf{Executive Summary}\\[0.2cm]
  The Florida Public Radio Emergency Network (FPREN) is a 24/7 automated emergency broadcast
  system hosted on a UF virtual machine. FPREN ingests National Weather Service and IPAWS alerts,
  converts them to speech, and streams emergency audio to broadcasters across nine Florida zones.
  A real-time Shiny R monitoring dashboard and Flask administrative interface support operations.
  This document formally requests three infrastructure changes from UF IT: (1) inbound firewall
  rules to open ports 80, 443, and 8000; (2) a CA-signed SSL certificate for the FPREN domain;
  and (3) GatorLink Shibboleth SSO integration to replace the current custom authentication system.
  These changes are required for FPREN to fulfill its public-safety mission, enable secure
  off-campus access, and align with UF IT security standards.
  \vspace{0.3cm}
}}
\end{center}

\newpage

<!-- ============================================================ -->
<!--  SECTION 1: PROJECT OVERVIEW                                 -->
<!-- ============================================================ -->

# Project Overview

## Mission and Purpose

The **Florida Public Radio Emergency Network (FPREN)** is a University of Florida project under
the College of Journalism and Communications / WUFT. Its mission is to provide automated,
continuous emergency weather broadcast capability for the state of Florida, serving emergency
management agencies, public broadcasters, and citizens.

FPREN operates as a 24/7 system that:

- Ingests live alerts from the **National Weather Service (NWS)** and **IPAWS** (Integrated
  Public Alert and Warning System) via official federal APIs
- Classifies and prioritizes alerts using UF's LiteLLM AI infrastructure
  (`api.ai.it.ufl.edu`)
- Converts alert text to spoken audio using Piper TTS and ElevenLabs for critical events
- Manages broadcast playlists per zone and streams audio over **Icecast2** to downstream
  broadcasters and the public
- Provides a **Shiny R real-time monitoring dashboard** with 14+ operational tabs
- Offers a **Flask administrative interface** for stream control, user management, and
  business continuity planning

FPREN is not a research prototype. It is an operational system providing public-safety
infrastructure for the state of Florida.

## Server Infrastructure

```{r server-table}
server_info <- data.frame(
  Component = c(
    "Host", "IP Address", "Operating System", "Hypervisor / Hosting",
    "Primary PI / Developer", "Department", "Institution",
    "Server Role"
  ),
  Detail = c(
    "UF Virtual Machine",
    "128.227.67.234",
    "Ubuntu 24.04 LTS",
    "UF Research Computing VM",
    "Lawrence Bornacelli (lawrence.bornace@ufl.edu)",
    "College of Journalism and Communications / WUFT",
    "University of Florida",
    "Production emergency broadcast server"
  ),
  stringsAsFactors = FALSE
)

kbl(
  server_info,
  booktabs = TRUE,
  col.names = c("Component", "Detail"),
  caption = "FPREN Server Infrastructure Summary"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2)
```

## Current Project Statistics

As of the date of this report, FPREN is live and actively serving operational data.

```{r stats-table}
stats <- data.frame(
  Metric = c(
    "Active NWS Alert Records",
    "Broadcast Zones (FL)",
    "FPREN-Specific Systemd Services",
    "Total Running Services",
    "Active User Accounts",
    "Registered Broadcast Assets",
    "USGS River Gauge Stations Monitored",
    "Florida Airport ASOS Stations Monitored",
    "Florida Cities with Weather History",
    "Weather History Retention Period"
  ),
  Value = c(
    "288",
    "9",
    "11",
    "17",
    "2 (admin + viewer)",
    "1",
    "513",
    "19",
    "16",
    "90 days"
  ),
  stringsAsFactors = FALSE
)

kbl(
  stats,
  booktabs = TRUE,
  col.names = c("Metric", "Value"),
  caption = "FPREN Live System Statistics"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE
  ) %>%
  column_spec(1) %>%
  column_spec(2, bold = TRUE)
```

\newpage

<!-- ============================================================ -->
<!--  SECTION 2: RUNNING SERVICES                                 -->
<!-- ============================================================ -->

# Active Services and Architecture

## Running Systemd Services

All 17 services listed below were confirmed running at the time this report was prepared.
Eleven are FPREN-specific; six are standard system services.

```{r services-table}
services <- data.frame(
  Service = c(
    "beacon-airport-delays",
    "beacon-extended-fetcher",
    "beacon-ipaws-fetcher",
    "beacon-mongo-tts",
    "beacon-obs-fetcher",
    "beacon-rivers-agent",
    "beacon-rivers-fetcher",
    "beacon-station-engine",
    "beacon-weather-service",
    "beacon-web-dashboard",
    "fpren-broadcast-generator",
    "fpren-multi-zone-streamer",
    "icecast2",
    "mongod",
    "nginx",
    "shiny-server",
    "zone-alert-tts"
  ),
  Type = c(
    "FPREN", "FPREN", "FPREN", "FPREN", "FPREN",
    "FPREN", "FPREN", "FPREN", "FPREN", "FPREN",
    "FPREN", "FPREN",
    "System", "System", "System", "System", "FPREN"
  ),
  Description = c(
    "Fetches FAA ATCSCC airport delay programs (outbound blocked --- see Section 4)",
    "Extended NWS forecast and zone data fetcher",
    "IPAWS/NWS alert ingestion, 2-minute polling interval",
    "MongoDB-to-TTS pipeline; queues alert audio conversion jobs",
    "Surface observation (METAR) data fetcher for 19 FL ASOS stations",
    "LiteLLM AI agent for USGS river gauge flood analysis",
    "USGS river gauge data fetcher for 513 FL gauges",
    "Core broadcast station engine; manages zone playlists",
    "Weather data aggregation and hourly snapshot service",
    "Shiny web dashboard backend process manager",
    "Multi-zone broadcast script and playlist generator",
    "Multi-zone Icecast2 stream manager (9 zone mounts)",
    "Icecast2 audio streaming server",
    "MongoDB document database (internal only, port 27017)",
    "Nginx reverse proxy (ports 80/443)",
    "Shiny R web application server (port 3838)",
    "Zone-specific TTS audio generation and queue processor"
  ),
  stringsAsFactors = FALSE
)

kbl(
  services,
  booktabs = TRUE,
  col.names = c("Service Name", "Type", "Description"),
  caption = "All 17 Active FPREN Systemd Services",
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE, monospace = TRUE) %>%
  column_spec(2) %>%
  column_spec(3) %>%
  row_spec(which(services$Type == "System"), background = "#f0f0f0")
```

## Internal Connectivity Status

All internal services are confirmed reachable on localhost. The table below documents the full
connectivity check results, including notes on protocols where TCP probes differ from actual
service behavior.

```{r connectivity-table}
conn <- data.frame(
  Target = c(
    "Shiny Server (localhost:3838)",
    "Flask Admin (localhost:5000)",
    "Icecast2 (localhost:8000)",
    "MongoDB (localhost:27017)",
    "RStudio Server (localhost:8787)",
    "SNMP Agent (localhost:161)",
    "Nginx port 80 (localhost)",
    "Nginx port 443 (localhost)",
    "UF NTP Server (128.227.30.254:123)",
    "UF LiteLLM API (api.ai.it.ufl.edu)",
    "UF DNS Primary (128.227.36.36:53)",
    "UF DNS Secondary (128.227.100.100:53)",
    "NWS Alerts API (api.weather.gov)",
    "NWS Points API (api.weather.gov)",
    "FAA ATCSCC API (soa.smext.faa.gov:443)",
    "Twilio API (api.twilio.com)",
    "ElevenLabs TTS (api.elevenlabs.io)",
    "US Census API (api.census.gov)",
    "NHC RSS (www.nhc.noaa.gov)"
  ),
  Status = c(
    "REACHABLE", "REACHABLE", "REACHABLE", "REACHABLE",
    "REACHABLE", "REFUSED", "REACHABLE", "REACHABLE",
    "TIMEOUT", "REACHABLE", "REFUSED", "TIMEOUT",
    "REACHABLE", "REACHABLE", "UNREACHABLE",
    "REACHABLE", "REACHABLE", "REACHABLE", "REACHABLE"
  ),
  Note = c(
    "Internal; not exposed externally",
    "Internal admin only",
    "Internal; port 8000 blocked externally by UF firewall",
    "Internal only; port 27017 not exposed",
    "Internal only",
    "Service not listening on TCP; SNMP uses UDP/161",
    "Nginx listening; port 80 blocked externally by UF firewall",
    "Nginx listening; port 443 blocked externally by UF firewall",
    "TCP probe only; NTP uses UDP/123 --- functionally OK",
    "Operational --- UF AI infrastructure",
    "DNS uses UDP; TCP refused is expected behavior",
    "DNS uses UDP; TCP probe timeout is expected behavior",
    "Operational",
    "Operational",
    "BLOCKED by UF IT outbound firewall --- see Section 4",
    "Operational --- SMS 2FA and alerts",
    "Operational --- TTS for critical alerts",
    "Operational --- Census demographics pipeline",
    "Operational --- NHC hurricane feed"
  ),
  stringsAsFactors = FALSE
)

status_colors <- ifelse(conn$Status == "REACHABLE", "statusgreen",
                 ifelse(conn$Status == "UNREACHABLE", "alertred", "uforange"))

kbl(
  conn,
  booktabs = TRUE,
  col.names = c("Target / Endpoint", "Status", "Notes"),
  caption = "FPREN Internal and External Connectivity Check Results",
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1) %>%
  column_spec(2, bold = TRUE) %>%
  column_spec(3) %>%
  row_spec(which(conn$Status == "UNREACHABLE"), background = "#fde8e8") %>%
  row_spec(which(conn$Status == "REFUSED"), background = "#fff8e1") %>%
  row_spec(which(conn$Status == "TIMEOUT"), background = "#fff8e1")
```

\newpage

<!-- ============================================================ -->
<!--  SECTION 3: COMPLETED FEATURES                               -->
<!-- ============================================================ -->

# Completed System Features

FPREN is a fully operational system. The following capabilities are currently implemented and
running in production.

```{r features-table}
features <- data.frame(
  N = 1:16,
  Feature = c(
    "Multi-Zone Broadcast System",
    "NWS / IPAWS Alert Ingestion",
    "Shiny R Monitoring Dashboard",
    "Flask Administrative Interface",
    "Business Continuity Planning (BCP)",
    "SNMP Monitoring Agent",
    "Emergency SMS Blast System",
    "Weather History Archive",
    "FL Rivers Monitoring",
    "Census and Demographics Pipeline",
    "FL511 Traffic Alerts",
    "Waze for Cities Integration",
    "Invite-Only Access Control",
    "Comprehensive Authentication",
    "Automated Daily Reports",
    "Airport Weather / Delay Monitoring"
  ),
  Description = c(
    "9 Florida broadcast zones, 11 systemd services, Piper TTS + ElevenLabs for critical alerts",
    "2-minute polling of NWS/IPAWS APIs; severity classification via UF LiteLLM AI",
    "Invite-only authentication; role-based access (admin/operator/viewer); 14+ operational tabs",
    "Stream control, user management, asset management, BCP report generation",
    "R Markdown PDFs per user/asset: evacuation routes, Waze overlays, weather risk, agency contacts, SMS checklists",
    "OID tree 1.3.6.1.4.1.64533, pass_persist agent, service status, user asset OID map",
    "Twilio-based role/phase to-do SMS with before/during/after emergency checklists",
    "Hourly METAR snapshots for 16 FL cities, 90-day retention policy",
    "513 USGS gauges monitored; LiteLLM AI flood analysis; flood stage alerts",
    "ACS 5-year Census data; vulnerability scoring; AI-generated impact analysis",
    "Statewide FL511 incident monitoring with county and severity filters",
    "Accident and jam hotspot proximity alerts near registered assets (awaiting UF CCP registration)",
    "No public login; token-based activation; 72-hour expiry with automatic account deletion",
    "bcrypt (cost 12), account lockout, inactivity auto-disable, SMS/email 2FA, full audit log",
    "Automated 2 PM daily weather, alerts, and BCP PDF generation",
    "METAR observations for 19 FL ASOS stations; FAA ATCSCC delay data currently blocked"
  ),
  stringsAsFactors = FALSE
)

kbl(
  features,
  booktabs = TRUE,
  col.names = c("#", "Feature", "Description"),
  caption = "FPREN Completed and Operational Features",
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1) %>%
  column_spec(2, bold = TRUE) %>%
  column_spec(3)
```

\newpage

<!-- ============================================================ -->
<!--  SECTION 4: FIREWALL REQUEST                                 -->
<!-- ============================================================ -->

# Firewall Access Request

## Summary of Requested Changes

FPREN requires the following firewall rule changes to fulfill its operational mission. The UF
external firewall currently blocks inbound access to ports 80, 443, and 8000 from off-campus,
and blocks one outbound connection to a federal API (`soa.smext.faa.gov:443`). These blocks
are the primary technical barrier preventing FPREN from serving its public-safety mission
outside the UF network.

```{r firewall-table}
fw <- data.frame(
  Port = c("80", "443", "8000", "161", "123", "443"),
  Proto = c("TCP", "TCP", "TCP", "UDP", "UDP", "TCP"),
  Direction = c(
    "Inbound",
    "Inbound",
    "Inbound",
    "Inbound",
    "Outbound",
    "Outbound to soa.smext.faa.gov"
  ),
  Current = c(
    "BLOCKED",
    "BLOCKED",
    "BLOCKED",
    "BLOCKED",
    "Open (assumed)",
    "BLOCKED"
  ),
  Requested = c(
    "OPEN",
    "OPEN",
    "OPEN (limited)",
    "OPEN (mgmt IP only)",
    "Confirm open",
    "OPEN"
  ),
  Service = c(
    "Nginx HTTP",
    "Nginx HTTPS",
    "Icecast2 Audio",
    "SNMP Agent",
    "NTP Sync",
    "FAA ATCSCC API"
  ),
  Justification = c(
    "Public dashboard access; redirect to 443. Required for Shibboleth HTTP challenges and Let's Encrypt ACME validation.",
    "Secure dashboard HTTPS. Required for Shibboleth SSO. Blocks all off-campus users currently.",
    "Public emergency audio streams. The /fpren main mount and all 9 zone mounts are inaccessible externally.",
    "Off-site SNMP polling from UF management station (PRTG/Nagios/Zabbix). Management IP restriction acceptable.",
    "System time accuracy for alert timestamps. NTP is UDP; TCP probe timeout was observed but service may be functional.",
    "FAA airport delay program data for emergency evacuation route planning. Federal public API."
  ),
  stringsAsFactors = FALSE
)

kbl(
  fw,
  booktabs = TRUE,
  col.names = c("Port", "Proto", "Direction", "Current", "Requested", "Service", "Justification"),
  caption = "FPREN Firewall Rule Change Requests",
) %>%
  kable_styling(
    latex_options = c("striped", "scale_down", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 8
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2) %>%
  column_spec(3) %>%
  column_spec(4, bold = TRUE) %>%
  column_spec(5, bold = TRUE) %>%
  column_spec(6) %>%
  column_spec(7) %>%
  row_spec(which(fw$Current == "BLOCKED"), background = "#fde8e8")
```

## Detailed Justification by Port

### Port 80 (TCP Inbound) --- HTTP / Nginx

Port 80 is required for:

1. **HTTP-to-HTTPS redirect.** Nginx listens on port 80 and issues a 301 redirect to port 443
   for all requests. Without port 80 open, users who type the FPREN URL without specifying
   HTTPS will receive a connection timeout rather than being redirected securely.
2. **ACME certificate validation.** If UF IT approves the use of Let's Encrypt alongside or
   instead of the UF InCommon certificate, the ACME HTTP-01 challenge requires that port 80
   be reachable from the internet for automated certificate renewal.
3. **Shibboleth SP pre-authentication flows.** Some Shibboleth SP configurations require
   HTTP reachability during initial handshake phases.

### Port 443 (TCP Inbound) --- HTTPS / Nginx / Shibboleth

This is the highest-priority firewall change. Port 443 being blocked means:

- **No off-campus dashboard access.** All FPREN monitoring must currently be performed on-campus
  or via VPN. Emergency managers, partner broadcasters, and UF staff who are in the field during
  a weather event cannot reach the dashboard.
- **Invite links do not work off-campus.** When administrators invite new users, the activation
  link points to the FPREN server on port 443. If the recipient is off-campus, the link times out
  and they cannot activate their account.
- **Shibboleth is impossible.** GatorLink SSO requires HTTPS. Without port 443 open, Phase 2 of
  the Shibboleth integration (Section 6) cannot proceed.
- **SSL certificate testing is blocked.** Even if a CA-signed certificate is installed, it cannot
  be verified from outside because the port is firewalled.

### Port 8000 (TCP Inbound) --- Icecast2 Audio Streaming

FPREN's primary mission is emergency audio broadcasting. Icecast2 serves the following mounts:

- `/fpren` --- main statewide emergency broadcast mount (public)
- `/north-florida`, `/central-florida`, `/south-florida` (and 6 additional zone mounts)

All nine zone streams are currently inaccessible to anyone outside the UF network. Emergency
broadcasters, partner radio stations, and public listeners cannot tune in to FPREN streams without
being on the UF campus network or VPN. This is a critical operational gap.

**Request:** Open port 8000 inbound, with consideration for rate limiting or IP allowlisting if
UF IT prefers a restricted initial deployment.

### Port 161 (UDP Inbound) --- SNMP Monitoring

FPREN includes a custom SNMP agent (OID tree `1.3.6.1.4.1.64533`) that exposes service health,
broadcast status, and user asset OIDs. Off-site SNMP management systems (PRTG, Nagios, Zabbix)
cannot poll these OIDs because UDP/161 is blocked.

**Request:** Open UDP/161 inbound from a specific UF management IP range only. We are prepared
to provide the management station IP(s) for allowlisting.

### Port 443 Outbound to soa.smext.faa.gov --- FAA ATCSCC API

The FAA Air Traffic Control System Command Center (ATCSCC) provides airport delay program data
via a public SOAP/REST API at `soa.smext.faa.gov:443`. FPREN fetches this data for the
`beacon-airport-delays` service to include airport delay information in emergency planning
(evacuation route impact, ground stop programs during severe weather, etc.).

This outbound connection is currently blocked by the UF firewall. The `beacon-airport-delays`
service runs but returns no data. This is a federal public API with no authentication requirement.

**Request:** Open outbound TCP/443 to `soa.smext.faa.gov`.

## Features Currently Blocked by Firewall

The following capabilities are fully implemented in FPREN code but non-functional due to the
firewall restrictions described above.

```{r blocked-features}
blocked <- data.frame(
  N = 1:6,
  Feature = c(
    "FAA Airport Delay Data",
    "Public Dashboard Access",
    "External Icecast Streams",
    "External SNMP Monitoring",
    "Waze CCP Feed",
    "Invite Links from Off-Campus"
  ),
  BlockedBy = c(
    "Outbound 443 to soa.smext.faa.gov blocked",
    "Inbound ports 80/443 blocked",
    "Inbound port 8000 blocked",
    "Inbound UDP 161 blocked",
    "UF not registered as Waze Connected Cities Partner",
    "Inbound port 443 blocked"
  ),
  Impact = c(
    "Airport delay programs unavailable; service runs but returns no data. Affects evacuation route planning during severe weather events.",
    "Dashboard inaccessible off-campus. Emergency managers and field staff cannot monitor FPREN during events. VPN required.",
    "All 9 zone emergency audio streams are internal-only. External broadcasters and public cannot receive audio.",
    "Cannot poll FPREN service health OIDs from off-site management systems.",
    "Traffic incident data (accidents and jams near evacuation routes) not populating. Feed URL is a placeholder.",
    "New users receiving invite emails cannot activate accounts if they are off-campus."
  ),
  stringsAsFactors = FALSE
)

kbl(
  blocked,
  booktabs = TRUE,
  col.names = c("#", "Blocked Feature", "Blocked By", "Operational Impact"),
  caption = "FPREN Features Currently Non-Functional Due to Access Restrictions",
) %>%
  kable_styling(
    latex_options = c("hold_position", "repeat_header"),
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1) %>%
  column_spec(2, bold = TRUE) %>%
  column_spec(3) %>%
  column_spec(4) %>%
  row_spec(0, background = "ufblue", color = "white") %>%
  row_spec(seq(1, nrow(blocked), 2), background = "#fde8e8") %>%
  row_spec(seq(2, nrow(blocked), 2), background = "#fff8e1")
```

\newpage

<!-- ============================================================ -->
<!--  SECTION 5: SSL CERTIFICATE REQUEST                          -->
<!-- ============================================================ -->

# SSL Certificate Request

## Current Status

Nginx is configured to serve HTTPS on port 443. However, the current certificate is either
self-signed or not yet installed at the system level. Because port 443 is firewalled externally,
browser validation of the certificate has not been possible from off-campus. Before port 443 is
opened, a CA-signed certificate must be in place.

## Certificate Requirements

FPREN requires a CA-signed SSL/TLS certificate for the following reasons:

1. **Browser trust.** Self-signed certificates generate browser warnings that are unacceptable
   for a public-safety dashboard.
2. **Shibboleth SSO prerequisite.** The UF Shibboleth IdP (`login.ufl.edu`) will not release
   attributes to a Service Provider using a self-signed certificate. A CA-signed certificate is
   a hard requirement for GatorLink SSO integration.
3. **UF InCommon compliance.** UF participates in the InCommon Federation. FPREN's SP registration
   will require a certificate from a trusted CA, ideally issued under the UF InCommon subscription.
4. **User trust.** Emergency managers and partner organizations who access the FPREN dashboard
   must be able to verify they are connecting to a legitimate UF-hosted service.

## Requested Certificate Options

The following options are presented in order of preference. We request UF IT guidance on which
is most appropriate.

```{r cert-options}
cert <- data.frame(
  Option = c(
    "UF InCommon SSL Certificate",
    "Let's Encrypt (ACME)",
    "UF Internal CA Certificate"
  ),
  Pros = c(
    "UF-managed; InCommon trusted by all major browsers and IdPs; ideal for Shibboleth SP; aligns with UF IT policy",
    "Free; automated renewal via Certbot; widely trusted; renewal requires port 80 open (ACME HTTP-01)",
    "Managed internally; no dependency on external CA; fast issuance"
  ),
  Cons = c(
    "Requires UF IT involvement for issuance; may require a fpren.ufl.edu DNS entry first",
    "Requires port 80 open for renewal; 90-day certificate requires automation; less preferred for Shibboleth",
    "May not be trusted by external Shibboleth federations; not ideal for public-facing dashboard"
  ),
  Preference = c("First choice", "Acceptable alternative", "Last resort"),
  stringsAsFactors = FALSE
)

kbl(
  cert,
  booktabs = TRUE,
  col.names = c("Certificate Option", "Advantages", "Disadvantages", "Preference"),
  caption = "SSL Certificate Options for FPREN"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2) %>%
  column_spec(3) %>%
  column_spec(4, bold = TRUE)
```

## DNS Hostname Request

A dedicated DNS hostname is needed for the certificate and for Shibboleth SP registration. We
request that UF IT assign a DNS A record pointing to `128.227.67.234`.

**Requested hostname:** `fpren.ufl.edu`

If `fpren.ufl.edu` is not available or not appropriate, alternative hostnames we would accept:

- `fpren-dashboard.ufl.edu`
- `emergency-broadcast.ufl.edu`
- `wuft-fpren.ufl.edu`

The DNS record should resolve to `128.227.67.234` (the UF VM). The Nginx configuration will be
updated to use the assigned hostname in the server block and in the Shibboleth SP configuration.

\newpage

<!-- ============================================================ -->
<!--  SECTION 6: SHIBBOLETH SSO REQUEST                          -->
<!-- ============================================================ -->

# GatorLink Shibboleth SSO Integration

## Current Authentication System

FPREN currently uses a custom authentication system built in Shiny R with MongoDB as the user
store. The system is functional and includes enterprise-grade security controls. Full details
of the current authentication implementation are provided in Section 7 (Security and Data
Classification).

While the current system is secure, migrating to GatorLink SSO offers the following advantages:

- Eliminates password management for UF-affiliated users
- Provides UF-enforced multi-factor authentication (DUO)
- Aligns with UF IT security policies for systems handling sensitive data
- Allows FPREN to auto-provision UF users without manual invite workflows
- Reduces the authentication attack surface by delegating credential verification to UF IAM

## Shibboleth Configuration Parameters

```{r shib-params}
shib <- data.frame(
  Parameter = c(
    "Protocol",
    "UF Identity Provider (IdP) URL",
    "SP Metadata URL (proposed)",
    "SP EntityID (proposed)",
    "Requested Attributes",
    "Attribute for Username",
    "Attribute for Email",
    "Attribute for Affiliation",
    "Default Role for New UF Users",
    "Nginx integration method",
    "Shibboleth SP package (Ubuntu 24.04)"
  ),
  Value = c(
    "SAML 2.0",
    "https://login.ufl.edu/idp/shibboleth",
    "https://fpren.ufl.edu/Shibboleth.sso/Metadata",
    "https://fpren.ufl.edu/shibboleth",
    "EPPN, mail, eduPersonAffiliation",
    "REMOTE_USER (set by Nginx from EPPN)",
    "mail (username@ufl.edu)",
    "eduPersonAffiliation (staff, faculty, member)",
    "viewer (read-only)",
    "Nginx FastCGI + shibd",
    "shibboleth-sp-utils, libapache2-mod-shib2"
  ),
  stringsAsFactors = FALSE
)

kbl(
  shib,
  booktabs = TRUE,
  col.names = c("Parameter", "Value / Specification"),
  caption = "FPREN Shibboleth SP Configuration Parameters"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, monospace = FALSE)
```

## Implementation Phases

The Shibboleth integration is structured in two phases. Phase 1 has been partially completed
without requiring UF IT involvement. Phase 2 requires UF IT action.

### Phase 1 --- Pre-Work (No UF IT Required)

The following tasks are completed or in progress on the FPREN server:

```{r phase1-table}
phase1 <- data.frame(
  Task = c(
    "Install shibboleth-sp-utils and libapache2-mod-shib2",
    "Generate SP signing and encryption key pair",
    "Configure shibboleth2.xml pointing to UF IdP",
    "Configure Nginx for Shibboleth FastCGI",
    "Build hybrid auth bridge in Shiny",
    "Auto-provision new GatorLink users as viewer role"
  ),
  Status = c(
    "Pending (awaiting port 443 open)",
    "Pending (awaiting DNS/cert)",
    "In progress",
    "In progress",
    "In progress",
    "Designed; implementation pending"
  ),
  Notes = c(
    "Package installation is straightforward on Ubuntu 24.04; no UF IT action needed",
    "Keys will be generated locally; public cert provided to UF IAM for SP registration",
    "EntityID and IdP URL configured; attribute mapping ready",
    "FastCGI wrapper script and location block prepared; requires DNS to finalize",
    "Shiny app checks REMOTE_USER header set by Nginx after Shibboleth auth",
    "New EPPN logins auto-create viewer account in MongoDB; admin can promote to operator/admin"
  ),
  stringsAsFactors = FALSE
)

kbl(
  phase1,
  booktabs = TRUE,
  col.names = c("Task", "Status", "Notes"),
  caption = "Shibboleth Phase 1 Tasks (FPREN-side, no UF IT required)",
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2) %>%
  column_spec(3)
```

### Phase 2 --- Requires UF IT Action

The following items require action or approval from UF IT / UF IAM.

```{r phase2-table}
phase2 <- data.frame(
  Task = c(
    "Complete UF Risk Assessment (IRM team)",
    "Obtain CA-signed SSL certificate",
    "Assign fpren.ufl.edu DNS A record",
    "Register FPREN SP at UF IAM registry",
    "Request Attribute Release Policy",
    "Open ports 80/443 on UF firewall",
    "Test with UF Beta IdP",
    "Production cutover"
  ),
  Owner = c(
    "UF IT / IRM",
    "UF IT",
    "UF IT / DNS",
    "UF IAM",
    "UF IAM",
    "UF IT Networking",
    "FPREN + UF IAM",
    "FPREN + UF IT"
  ),
  Priority = c(
    "High",
    "High",
    "High",
    "High",
    "High",
    "Critical",
    "Medium",
    "Low"
  ),
  Notes = c(
    "IRM review for system handling user PII (email, phone). Data classification in Section 7.",
    "UF InCommon preferred; see Section 5.",
    "Required before SP registration and cert issuance.",
    "Provide SP metadata XML generated in Phase 1.",
    "Request EPPN, mail, eduPersonAffiliation attributes.",
    "Prerequisite for all external access; see Section 4.",
    "Validate full login flow before production.",
    "Switch production traffic to Shibboleth auth; retain legacy auth for non-UF users."
  ),
  stringsAsFactors = FALSE
)

kbl(
  phase2,
  booktabs = TRUE,
  col.names = c("Task", "Owner", "Priority", "Notes"),
  caption = "Shibboleth Phase 2 Tasks (Requires UF IT Action)",
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2) %>%
  column_spec(3, bold = TRUE) %>%
  column_spec(4) %>%
  row_spec(which(phase2$Priority == "Critical"), background = "#fde8e8") %>%
  row_spec(which(phase2$Priority == "High"), background = "#fff8e1")
```

## Hybrid Authentication Architecture

FPREN will maintain a hybrid authentication model after Shibboleth integration. This preserves
access for non-UF partners (emergency management agencies, partner broadcasters) who do not have
GatorLink credentials.

The authentication flow will be:

1. User visits `https://fpren.ufl.edu`
2. Nginx checks for a valid `_shibsession_*` cookie
3. If present and valid: Nginx sets `REMOTE_USER` header; Shiny reads it and maps EPPN to
   MongoDB user record (auto-creating if first login)
4. If not present: Nginx presents the FPREN custom login form (legacy path for non-UF users
   with invite tokens)
5. Admin dashboard retains ability to create invite-only accounts for non-GatorLink users
   (e.g., external emergency managers)

```{r auth-flow-note, results='asis'}
cat("\\vspace{0.3cm}")
cat("\\colorbox{lightgray}{\\parbox{0.92\\textwidth}{")
cat("\\vspace{0.2cm}")
cat("\\textbf{Note for UF IT:} The hybrid model means Shibboleth protects the primary login path ")
cat("but does not replace all authentication. Non-UF users will continue to use the invite-only ")
cat("token system. The Shiny application checks \\texttt{REMOTE\\_USER} first; if not set, it ")
cat("falls through to the legacy credential check against MongoDB. Both paths use bcrypt ")
cat("password verification or Shibboleth session tokens respectively.")
cat("\\vspace{0.2cm}")
cat("}}")
```

## Questions for UF IT / UF IAM

The following questions require clarification from UF IT before FPREN can complete the
Shibboleth SP configuration.

```{r shib-questions}
questions <- data.frame(
  N = 1:5,
  Question = c(
    "SP EntityID format",
    "DNS / hostname assignment",
    "Attribute release policy",
    "DUO 2FA at Shibboleth level",
    "Nginx + shibd method approval"
  ),
  Detail = c(
    "Should the SP EntityID be https://fpren.ufl.edu/shibboleth (hostname-based) or IP-based (https://128.227.67.234/shibboleth)? Hostname-based is strongly preferred.",
    "Can UF IT assign a fpren.ufl.edu DNS A record pointing to 128.227.67.234? This is required before SP registration and certificate issuance.",
    "Which UF attributes will be released to the FPREN SP? We require at minimum: eduPersonPrincipalName (EPPN), mail, and eduPersonAffiliation.",
    "Is DUO 2FA enforced at the Shibboleth IdP level for all SP sessions? If yes, FPREN does not need to implement its own MFA for UF users (currently uses SMS/email 2FA via Twilio).",
    "Is Nginx with shibd FastCGI the UF-approved Shibboleth SP method for Ubuntu 24.04 LTS? Alternatively, is mod_shib with Apache preferred?"
  ),
  stringsAsFactors = FALSE
)

kbl(
  questions,
  booktabs = TRUE,
  col.names = c("#", "Question", "Detail"),
  caption = "Open Questions for UF IT / UF IAM Regarding Shibboleth Integration"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1) %>%
  column_spec(2, bold = TRUE) %>%
  column_spec(3)
```

\newpage

<!-- ============================================================ -->
<!--  SECTION 7: SECURITY AND DATA CLASSIFICATION                 -->
<!-- ============================================================ -->

# Security and Data Classification

## Current Authentication Controls

FPREN implements enterprise-grade authentication controls in its custom Shiny R + MongoDB system.
These controls meet or exceed standard web application security requirements and will remain in
place for non-Shibboleth users after SSO integration.

```{r auth-controls}
auth <- data.frame(
  Control = c(
    "Password hashing",
    "Account lockout",
    "Inactivity auto-disable",
    "Invite token expiry",
    "SMS phone verification",
    "Email verification",
    "First-login password change",
    "Session timeout",
    "Audit logging",
    "Role-based access control",
    "Group invite controls",
    "Access model"
  ),
  Implementation = c(
    "bcrypt with cost factor 12",
    "3 failed attempts triggers 24-hour account lock",
    "Accounts auto-disabled after 6 months of inactivity",
    "72-hour expiry; account auto-deleted if not activated",
    "Twilio 6-digit code; 10-minute expiry",
    "SMTP 6-digit code; verified before account activation",
    "Enforced on first successful login",
    "5-minute browser inactivity triggers automatic logout (JavaScript)",
    "Full audit log in MongoDB user_audit_log collection",
    "admin / operator / viewer role hierarchy",
    "Per-admin group invite enable/disable control",
    "Invite-only; no public login form exposed"
  ),
  stringsAsFactors = FALSE
)

kbl(
  auth,
  booktabs = TRUE,
  col.names = c("Security Control", "Implementation Detail"),
  caption = "FPREN Current Authentication Security Controls"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2)
```

## User Account Data Fields

The following fields are stored per user account in MongoDB. This data is relevant to the UF IRM
risk assessment.

```{r user-fields}
fields <- data.frame(
  Field = c(
    "username", "email", "phone", "role",
    "profession", "bcrypt_hash", "email_verified",
    "phone_verified", "last_login", "failed_attempts",
    "locked_until", "created_at", "created_by",
    "invite_token", "invite_expires", "auth_source"
  ),
  Type = c(
    "String", "String (PII)", "String (PII)", "Enum",
    "String", "String (hashed)", "Boolean",
    "Boolean", "DateTime", "Integer",
    "DateTime", "DateTime", "String",
    "String (token)", "DateTime", "Enum"
  ),
  Description = c(
    "Unique username",
    "UF or personal email address",
    "Mobile phone number for SMS 2FA",
    "admin, operator, or viewer",
    "User's professional role (e.g., Engineer, Manager)",
    "bcrypt hash of password; plaintext never stored",
    "Whether email address has been verified",
    "Whether phone number has been verified via SMS",
    "Timestamp of most recent successful login",
    "Count of consecutive failed login attempts",
    "Timestamp until account is locked (after 3 failures)",
    "Account creation timestamp",
    "Username of admin who created this account",
    "Time-limited invite token (cleared after activation)",
    "Expiry timestamp for invite token",
    "local (custom auth) or shibboleth (SSO)"
  ),
  stringsAsFactors = FALSE
)

kbl(
  fields,
  booktabs = TRUE,
  col.names = c("Field", "Type / Classification", "Description"),
  caption = "FPREN MongoDB User Account Schema",
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE, monospace = TRUE) %>%
  column_spec(2) %>%
  column_spec(3) %>%
  row_spec(which(grepl("PII", fields$Type)), background = "#fff8e1")
```

## Data Classification

```{r data-class}
data_class <- data.frame(
  DataType = c(
    "NWS / IPAWS weather alert data",
    "Broadcast audio streams",
    "User account records (email, phone, role)",
    "Broadcast asset locations",
    "MongoDB database",
    "Audit logs",
    "Business Continuity Plan PDFs"
  ),
  Classification = c(
    "PUBLIC",
    "PUBLIC",
    "RESTRICTED",
    "SENSITIVE",
    "INTERNAL ONLY",
    "INTERNAL ONLY",
    "SENSITIVE"
  ),
  Rationale = c(
    "Federal public domain data; no PII",
    "Public emergency broadcast; no PII",
    "Contains UF staff PII: email addresses and phone numbers",
    "Physical addresses and lat/lon of UF broadcast facilities",
    "Port 27017 not exposed; internal access only",
    "Contains login timestamps, IP-adjacent data",
    "Contains asset locations, agency contacts, evacuation routes"
  ),
  stringsAsFactors = FALSE
)

kbl(
  data_class,
  booktabs = TRUE,
  col.names = c("Data Type", "Classification", "Rationale"),
  caption = "FPREN Data Classification Summary"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, bold = TRUE) %>%
  column_spec(3) %>%
  row_spec(which(data_class$Classification == "RESTRICTED"), background = "#fff8e1") %>%
  row_spec(which(data_class$Classification == "SENSITIVE"), background = "#fde8e8")
```

**Regulatory compliance note:** FPREN does not process, store, or transmit FERPA-protected
student records, HIPAA-covered health information, or PCI-DSS payment card data. The only
sensitive data is UF staff contact information (email and phone) used for system access and
emergency notifications.

\newpage

<!-- ============================================================ -->
<!--  SECTION 8: PLANNED FEATURES                                 -->
<!-- ============================================================ -->

# Planned Features and Future Roadmap

The following features are planned for future FPREN development. Several have direct dependencies
on the infrastructure changes requested in this document.

```{r roadmap-table}
roadmap <- data.frame(
  Feature = c(
    "Travel Buddy",
    "Social Media Integration",
    "Public-Facing Alert Map",
    "Mobile Companion App",
    "GatorLink SSO (Phase 2)",
    "Enhanced AI/ML Pipeline",
    "Desktop Notification Integration",
    "Alarms and SNMP Dashboard Tab"
  ),
  Status = c(
    "Planned",
    "Planned",
    "Planned",
    "Planned",
    "Phase 1 in progress",
    "Planned",
    "Partially built",
    "Placeholder exists"
  ),
  UF_IT_Dependency = c(
    "Ports 80/443 (for off-campus use)",
    "Ports 80/443 (for posting to social platforms)",
    "Ports 80/443 (public URL required)",
    "Shibboleth SSO + ports 80/443",
    "All items in Section 6 Phase 2",
    "None (internal UF LiteLLM API already operational)",
    "None (internal enhancement)",
    "Port 161 UDP (for SNMP polling)"
  ),
  Description = c(
    "Multi-user trip coordination for broadcast crews. Route planning with NWS forecasts, FL511 alerts, and FPREN zone coverage along travel corridors.",
    "Automated posting of FPREN alerts to X/Twitter, Facebook, RSS, and Mastodon. Admin-configurable severity thresholds for auto-post vs. approval.",
    "Public Leaflet/Mapbox map showing live NWS alerts, river gauges, Waze incidents, and FPREN broadcast zone status. Embedded audio player for live stream.",
    "React Native iOS/Android app for FPREN staff. Push notifications for Extreme/Severe alerts, stream monitoring, BCP checklists, GatorLink SSO auth.",
    "Full GatorLink SSO integration per Section 6. Requires UF IT firewall, DNS, cert, SP registration, and attribute release policy.",
    "Predictive severity escalation, NLP zone routing, automated situation reports every 6 hours during active events.",
    "Windows/Mac system tray integration and push notifications for the existing Tkinter desktop dashboard.",
    "Real-time SNMP OID display in Shiny Alarms tab, threshold-based alert rules, integration with external monitoring systems."
  ),
  stringsAsFactors = FALSE
)

kbl(
  roadmap,
  booktabs = TRUE,
  col.names = c("Feature", "Status", "UF IT Dependency", "Description"),
  caption = "FPREN Planned Features and UF IT Dependencies",
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "repeat_header"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2) %>%
  column_spec(3) %>%
  column_spec(4)
```

\newpage

<!-- ============================================================ -->
<!--  SECTION 9: SUMMARY AND REQUESTS                             -->
<!-- ============================================================ -->

# Summary of Requests

## Action Items for UF IT

The following table consolidates all items requiring UF IT action, in priority order.

```{r action-items}
actions <- data.frame(
  Priority = c(1, 2, 3, 4, 5, 6, 7, 8),
  Action = c(
    "Open inbound TCP/443 on UF firewall",
    "Open inbound TCP/80 on UF firewall",
    "Assign fpren.ufl.edu DNS A record to 128.227.67.234",
    "Issue CA-signed SSL certificate (UF InCommon preferred)",
    "Open inbound TCP/8000 on UF firewall (Icecast audio)",
    "Register FPREN SP at UF IAM registry and configure attribute release",
    "Open outbound TCP/443 to soa.smext.faa.gov (FAA API)",
    "Open inbound UDP/161 for SNMP (management IP range only)"
  ),
  Team = c(
    "UF IT Networking",
    "UF IT Networking",
    "UF IT / DNS",
    "UF IT",
    "UF IT Networking",
    "UF IAM",
    "UF IT Networking",
    "UF IT Networking"
  ),
  Urgency = c(
    "Critical",
    "Critical",
    "Critical",
    "High",
    "High",
    "High",
    "Medium",
    "Low"
  ),
  Notes = c(
    "Prerequisite for all external access, SSL, and Shibboleth. Highest priority.",
    "Required for HTTP-to-HTTPS redirect and ACME cert renewal.",
    "Required before SSL cert issuance and SP registration.",
    "Required before port 443 is opened to avoid browser cert warnings.",
    "Required for public emergency audio stream access.",
    "Requires DNS and cert to be in place first.",
    "Enables FAA airport delay data for emergency planning.",
    "Enables off-site SNMP health monitoring."
  ),
  stringsAsFactors = FALSE
)

kbl(
  actions,
  booktabs = TRUE,
  col.names = c("Priority", "Action Required", "UF IT Team", "Urgency", "Notes"),
  caption = "Consolidated Action Items for UF IT --- Priority Order"
) %>%
  kable_styling(
    latex_options = c("hold_position"),
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2) %>%
  column_spec(3) %>%
  column_spec(4, bold = TRUE) %>%
  column_spec(5) %>%
  row_spec(0, background = "ufblue", color = "white") %>%
  row_spec(1:2, background = "#fde8e8") %>%
  row_spec(3:4, background = "#fde8e8") %>%
  row_spec(5:6, background = "#fff8e1") %>%
  row_spec(7:8, background = "#f0f8e8")
```

## Contact Information

For questions, additional documentation, or to schedule a technical walkthrough of the FPREN
system, please contact:

\vspace{0.3cm}

\begin{center}
\colorbox{lightgray}{\parbox{0.6\textwidth}{
\vspace{0.3cm}
\begin{center}
\textbf{Lawrence Bornacelli}\\
\textit{Principal Investigator / Lead Developer, FPREN}\\
College of Journalism and Communications / WUFT\\
University of Florida\\
\href{mailto:lawrence.bornace@ufl.edu}{lawrence.bornace@ufl.edu}\\
Server: \texttt{128.227.67.234}
\end{center}
\vspace{0.3cm}
}}
\end{center}

\vspace{0.5cm}

\begin{center}
\colorbox{ufblue}{\parbox{0.92\textwidth}{
\vspace{0.4cm}
\begin{center}
\textcolor{white}{\textbf{Thank you for your consideration.}}\\[0.2cm]
\textcolor{uforange}{\small FPREN is an operational public-safety system serving the state of Florida.}\\[0.1cm]
\textcolor{white}{\small The infrastructure changes requested in this document are prerequisite to FPREN}\\
\textcolor{white}{\small fulfilling its mission of delivering emergency broadcast coverage to all Floridians,}\\
\textcolor{white}{\small not only those with access to the UF campus network.}
\end{center}
\vspace{0.4cm}
}}
\end{center}

\newpage

<!-- ============================================================ -->
<!--  APPENDIX A: BROADCAST ZONES                                 -->
<!-- ============================================================ -->

# Appendix A: FPREN Broadcast Zones

FPREN manages nine Florida broadcast zones. Each zone has a dedicated Icecast2 mount point, a
systemd-managed streaming process, and independent alert queues.

```{r zones-table}
zones <- data.frame(
  Zone = c(
    "north-florida",
    "northeast-florida",
    "northwest-florida",
    "central-florida",
    "east-central-florida",
    "west-central-florida",
    "southwest-florida",
    "southeast-florida",
    "south-florida"
  ),
  IcecastMount = c(
    "/north-florida",
    "/northeast-florida",
    "/northwest-florida",
    "/central-florida",
    "/east-central-florida",
    "/west-central-florida",
    "/southwest-florida",
    "/southeast-florida",
    "/south-florida"
  ),
  ExampleCounties = c(
    "Alachua, Gainesville area",
    "Duval (Jacksonville), St. Johns",
    "Leon (Tallahassee), Escambia",
    "Orange (Orlando), Osceola",
    "Brevard, Indian River",
    "Hillsborough (Tampa), Pinellas",
    "Lee (Fort Myers), Collier",
    "Palm Beach, Martin",
    "Miami-Dade, Broward, Monroe"
  ),
  ExternalAccess = c(
    rep("BLOCKED (port 8000)", 9)
  ),
  stringsAsFactors = FALSE
)

kbl(
  zones,
  booktabs = TRUE,
  col.names = c("Zone Name", "Icecast Mount", "Example Counties", "External Access Status"),
  caption = "FPREN Florida Broadcast Zones and Icecast Mount Points"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    stripe_color = "lightgray",
    full_width = TRUE,
    font_size = 9
  ) %>%
  column_spec(1, bold = TRUE, monospace = TRUE) %>%
  column_spec(2, monospace = TRUE) %>%
  column_spec(3) %>%
  column_spec(4, bold = TRUE) %>%
  row_spec(1:9, color = "alertred")
```

The main statewide mount `/fpren` serves a consolidated emergency broadcast. All nine zone mounts
plus the main mount are inaccessible externally until port 8000 is opened on the UF firewall.

\newpage

<!-- ============================================================ -->
<!--  APPENDIX B: NGINX CONFIGURATION OVERVIEW                   -->
<!-- ============================================================ -->

# Appendix B: Nginx Configuration Overview

Nginx serves as the reverse proxy for all FPREN web services. The current configuration structure
is summarized below. This will be extended with Shibboleth FastCGI blocks once port 443 is open
and the SSL certificate is installed.

```{r nginx-config, results='asis'}
cat("\\begin{verbatim}\n")
cat("# FPREN Nginx Configuration (summary)\n")
cat("# Full configuration available on request\n\n")
cat("server {\n")
cat("    listen 80;                         # Inbound blocked by UF firewall\n")
cat("    server_name fpren.ufl.edu;         # Pending DNS assignment\n")
cat("    return 301 https://$host$request_uri;  # Redirect to HTTPS\n")
cat("}\n\n")
cat("server {\n")
cat("    listen 443 ssl;                    # Inbound blocked by UF firewall\n")
cat("    server_name fpren.ufl.edu;\n\n")
cat("    ssl_certificate     /etc/ssl/fpren/fpren.ufl.edu.crt;  # Pending UF InCommon cert\n")
cat("    ssl_certificate_key /etc/ssl/fpren/fpren.ufl.edu.key;\n\n")
cat("    # Shiny R dashboard (proxy to localhost:3838)\n")
cat("    location / {\n")
cat("        proxy_pass http://127.0.0.1:3838;\n")
cat("        proxy_http_version 1.1;\n")
cat("        proxy_set_header Upgrade $http_upgrade;\n")
cat("        proxy_set_header Connection 'upgrade';\n")
cat("    }\n\n")
cat("    # Flask admin interface\n")
cat("    location /admin {\n")
cat("        proxy_pass http://127.0.0.1:5000;\n")
cat("    }\n\n")
cat("    # Shibboleth FastCGI (Phase 2 --- pending UF IAM registration)\n")
cat("    # location /Shibboleth.sso {\n")
cat("    #     fastcgi_pass unix:/run/shibboleth/shibauthorizer.sock;\n")
cat("    # }\n")
cat("}\n")
cat("\\end{verbatim}\n")
```

\newpage

<!-- ============================================================ -->
<!--  APPENDIX C: LIVE CONNECTIVITY DATA (IF AVAILABLE)          -->
<!-- ============================================================ -->

# Appendix C: Live Connectivity Data

```{r live-data-section, results='asis'}
if (!is.null(live_data)) {
  cat("The following data was read from \\texttt{/tmp/fpren\\_access\\_check.json} at render time,\n")
  cat("reflecting the live connectivity state of the FPREN server.\\vspace{0.3cm}\n\n")

  # Try to render as a table if it has expected structure
  tryCatch({
    if (is.data.frame(live_data) || is.list(live_data)) {
      df <- as.data.frame(live_data)
      kbl(
        df,
        booktabs = TRUE,
        caption = "Live FPREN Connectivity Check Results (from /tmp/fpren\\_access\\_check.json)",
      ) %>%
        kable_styling(
          latex_options = c("striped", "hold_position", "scale_down"),
          stripe_color = "lightgray",
          full_width = TRUE,
          font_size = 9
        ) %>%
        print()
    }
  }, error = function(e) {
    cat("Live data was present but could not be rendered as a table. Raw structure:\\vspace{0.2cm}\n\n")
    cat("\\begin{verbatim}\n")
    cat(paste(capture.output(str(live_data)), collapse = "\n"))
    cat("\n\\end{verbatim}\n")
  })
} else {
  cat("\\colorbox{lightgray}{\\parbox{0.92\\textwidth}{\\vspace{0.2cm}\n")
  cat("\\textbf{Note:} No live connectivity data file was found at \\texttt{/tmp/fpren\\_access\\_check.json}\n")
  cat("at the time this report was rendered. The connectivity data in Section 2.2 reflects\n")
  cat("the most recent manual check performed prior to this report generation. To include live\n")
  cat("connectivity data, run the FPREN connectivity check script and save the output to\n")
  cat("\\texttt{/tmp/fpren\\_access\\_check.json} before rendering this document.\n")
  cat("\\vspace{0.2cm}}}\n")
}
```

\vspace{1cm}

---

\begin{center}
\small\textcolor{midgray}{
This document was prepared by Lawrence Bornacelli for submission to UF Information Technology.\\
Florida Public Radio Emergency Network (FPREN) --- College of Journalism and Communications / WUFT\\
University of Florida --- \texttt{128.227.67.234}\\
\textbf{CONFIDENTIAL --- UF Internal Use Only}
}
\end{center}
