---
title: "FPREN Weather Trends Report"
subtitle: "`r params$city_name` — `r params$start_date` to `r params$end_date`"
date: "Generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p UTC')`"
geometry: "margin=1in"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    latex_engine: xelatex
    keep_tex: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{xcolor}
  - \usepackage{longtable}
  - \definecolor{fprenblue}{RGB}{0, 70, 127}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\textcolor{fprenblue}{\textbf{FPREN}}}
  - \fancyhead[C]{\textcolor{fprenblue}{Weather Trends}}
  - \fancyhead[R]{\textcolor{gray}{`r params$city_name`}}
  - \renewcommand{\headrulewidth}{0.4pt}
params:
  icao:       "KGNV"
  city_name:  "Gainesville"
  start_date: ""
  end_date:   ""
  mongo_uri:  "mongodb://localhost:27017/"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 4)
suppressPackageStartupMessages({
  library(mongolite)
  library(dplyr)
  library(lubridate)
  library(ggplot2)
  library(scales)
  library(knitr)
  library(kableExtra)
})

start_d <- if (nchar(params$start_date) > 0) params$start_date else
             format(Sys.Date() - 30, "%Y-%m-%d")
end_d   <- if (nchar(params$end_date)   > 0) params$end_date   else
             format(Sys.Date(),        "%Y-%m-%d")

# Extend end to include the full day
end_dt_str <- paste0(end_d, "T23:59:59Z")

query <- sprintf(
  '{"icao":"%s","timestamp":{"$gte":"%sT00:00:00Z","$lte":"%s"}}',
  params$icao, start_d, end_dt_str
)

col <- tryCatch(
  mongo(collection = "weather_history", db = "weather_rss", url = params$mongo_uri),
  error = function(e) NULL
)

df <- if (!is.null(col)) {
  tryCatch({
    d <- col$find(query, fields = '{"_id":0}',
                  sort = '{"timestamp":1}')
    col$disconnect()
    d
  }, error = function(e) {
    tryCatch(col$disconnect(), error=function(e2) NULL)
    data.frame()
  })
} else data.frame()

n_records <- nrow(df)

if (n_records > 0) {
  df$ts <- as.POSIXct(df$timestamp, tz = "UTC", format = "%Y-%m-%dT%H:%M:%SZ")
  df$date <- as.Date(df$ts)
  df$flight_cat <- factor(df$flight_cat,
    levels = c("VFR","MVFR","IFR","LIFR","UNK"), exclude = NULL)
}

CAT_COLOURS <- c(VFR="#1a6bb5", MVFR="#b5860a", IFR="#c0460a",
                 LIFR="#8b0000", UNK="#888888")
```

\newpage

# Summary

**Station:** `r params$icao` — `r params$city_name`
**Period:** `r start_d` to `r end_d`
**Records:** `r n_records`
**Generated:** `r format(Sys.time(), "%Y-%m-%d %H:%M UTC")`

```{r no-data, results='asis'}
if (n_records == 0) {
  cat("\n> **No weather history data found for this station and date range.**\n\n")
  cat("> The `fpren-weather-history.timer` service must run for at least one hour")
  cat(" before data is available.\n")
  knitr::knit_exit()
}
```

```{r summary-stats}
has_wind <- "wind_speed" %in% colnames(df)
has_vis  <- "visibility" %in% colnames(df)

metrics <- c("Temp Min (°F)","Temp Max (°F)","Temp Avg (°F)",
             "Feels Like Avg (°F)","Humidity Avg (%)")
values  <- c(round(min(df$temp_f,      na.rm=TRUE), 1),
             round(max(df$temp_f,      na.rm=TRUE), 1),
             round(mean(df$temp_f,     na.rm=TRUE), 1),
             round(mean(df$feels_like_f,na.rm=TRUE), 1),
             round(mean(df$humidity,   na.rm=TRUE), 1))
if (has_wind) {
  metrics <- c(metrics, "Wind Max (kt)", "Wind Avg (kt)")
  values  <- c(values,
               round(max(df$wind_speed,  na.rm=TRUE), 1),
               round(mean(df$wind_speed, na.rm=TRUE), 1))
}
if (has_vis) {
  metrics <- c(metrics, "Visibility Min (mi)", "Visibility Avg (mi)")
  values  <- c(values,
               round(min(df$visibility,  na.rm=TRUE), 1),
               round(mean(df$visibility, na.rm=TRUE), 1))
}
tbl <- data.frame(Metric=metrics, Value=values, stringsAsFactors=FALSE)
kable(tbl, booktabs=TRUE, row.names=FALSE,
      caption="Summary statistics for the selected period") %>%
  kable_styling(latex_options=c("hold_position"), font_size=10)
```

\newpage

# Temperature Trend

```{r temp-trend, fig.cap="Temperature over time. Red = feels-like temperature."}
ggplot(df, aes(x = ts)) +
  geom_line(aes(y = temp_f,      colour = "Actual"),     linewidth = 0.7, alpha = 0.9) +
  geom_line(aes(y = feels_like_f, colour = "Feels Like"), linewidth = 0.5, alpha = 0.7,
            linetype = "dashed") +
  scale_colour_manual(values = c(Actual="#1a6bb5", "Feels Like"="#c0392b"),
                      name = NULL) +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "3 days") +
  labs(x = NULL, y = "Temperature (°F)",
       title = paste0(params$city_name, " — Temperature ", start_d, " to ", end_d)) +
  theme_bw(base_size = 11) +
  theme(legend.position = "top", axis.text.x = element_text(angle=30, hjust=1))
```

\newpage

# Wind Speed Trend

```{r wind-trend, fig.cap="Wind speed (kt) over time. Background shading shows flight category."}
if (has_wind) {
  print(
    ggplot(df, aes(x = ts, y = wind_speed)) +
      geom_rect(data = df,
        aes(xmin = ts, xmax = lead(ts, default = last(ts)),
            ymin = -Inf, ymax = Inf, fill = flight_cat),
        alpha = 0.15, inherit.aes = FALSE) +
      geom_line(colour = "#2980b9", linewidth = 0.8) +
      scale_fill_manual(values = CAT_COLOURS, name = "Flight Cat", na.value = "#dddddd") +
      scale_x_datetime(date_labels = "%b %d", date_breaks = "3 days") +
      labs(x = NULL, y = "Wind Speed (kt)",
           title = paste0(params$city_name, " - Wind Speed ", start_d, " to ", end_d)) +
      theme_bw(base_size = 11) +
      theme(legend.position = "top", axis.text.x = element_text(angle=30, hjust=1))
  )
} else {
  cat("> Wind speed data not available for this station.\n")
}
```

\newpage

# Humidity Trend

```{r humidity-trend, fig.cap="Relative humidity (%) over time."}
ggplot(df %>% filter(!is.na(humidity)), aes(x = ts, y = humidity)) +
  geom_line(colour = "#27ae60", linewidth = 0.7, alpha = 0.9) +
  geom_hline(yintercept = 80, linetype="dashed", colour="#e67e22", alpha=0.7) +
  annotate("text", x = min(df$ts), y = 82, label="80% threshold",
           hjust=0, size=3, colour="#e67e22") +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "3 days") +
  scale_y_continuous(limits = c(0, 100), labels = scales::percent_format(scale=1)) +
  labs(x = NULL, y = "Relative Humidity (%)",
       title = paste0(params$city_name, " — Humidity ", start_d, " to ", end_d)) +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle=30, hjust=1))
```

\newpage

# Flight Category Distribution

```{r flt-cat-dist, fig.width=5, fig.height=4, fig.align='center', fig.cap="Distribution of flight categories over the report period."}
cat_counts <- df %>%
  count(flight_cat, .drop=FALSE) %>%
  filter(!is.na(flight_cat), flight_cat != "UNK" | n > 0) %>%
  mutate(
    pct   = round(n / sum(n) * 100, 1),
    label = paste0(flight_cat, "\n", pct, "%")
  )

ggplot(cat_counts, aes(x="", y=n, fill=flight_cat)) +
  geom_bar(stat="identity", width=1, colour="white") +
  coord_polar("y", start=0) +
  scale_fill_manual(values=CAT_COLOURS, name="Category") +
  geom_text(aes(label=label),
            position=position_stack(vjust=0.5), size=3.5, colour="white") +
  labs(title = "Flight Category Distribution") +
  theme_void(base_size=11) +
  theme(legend.position="right")
```

```{r flt-cat-table}
kable(cat_counts %>% select(flight_cat, n, pct) %>%
        rename(Category=flight_cat, Count=n, `Pct %`=pct),
      booktabs=TRUE, row.names=FALSE,
      caption="Flight category counts and percentages") %>%
  kable_styling(latex_options=c("hold_position"), font_size=10)
```

\newpage

# Notable IFR / LIFR Events

```{r ifr-events, results='asis'}
ifr_cols <- intersect(c("ts","flight_cat","temp_f","humidity","visibility","wx_desc"),
                      colnames(df))
ifr_df <- df %>%
  filter(flight_cat %in% c("IFR","LIFR")) %>%
  select(all_of(ifr_cols)) %>%
  mutate(ts = format(ts, "%Y-%m-%d %H:%M UTC"))

if (nrow(ifr_df) == 0) {
  cat("> No IFR or LIFR periods recorded during this window.\n")
} else {
  cat(paste0("There were **", nrow(ifr_df),
    "** IFR/LIFR observations during this period.\n\n"))
  rename_map <- c("Time"="ts", "Category"="flight_cat", "Temp (F)"="temp_f",
                  "RH (%)"="humidity", "Vis (mi)"="visibility", "Description"="wx_desc")
  rename_map <- rename_map[rename_map %in% colnames(ifr_df)]
  display <- ifr_df %>% rename(!!!rename_map)
  print(kable(display, booktabs=TRUE, longtable=TRUE,
              caption="IFR and LIFR observation periods") %>%
    kable_styling(latex_options=c("striped","hold_position","repeat_header"),
                  font_size=8) %>%
    row_spec(which(display$Category == "LIFR"), bold=TRUE, color="white",
             background="#8b0000") %>%
    row_spec(which(display$Category == "IFR"),  bold=FALSE, color="white",
             background="#c0460a"))
}
```

---

*Report generated by FPREN R reporting system.*
*Data source: `weather_history` MongoDB collection (hourly METAR snapshots).*
*Station: `r params$icao` | Period: `r start_d` to `r end_d`*
*Server: `r Sys.info()[["nodename"]]` | R `r R.version.string`*
